Cooling Requirements for the Vertical Shear Instability in Protoplanetary Disks

### 2015-07-08 linear_iso.tex
more reply edits

 In Appendix \ref{global_corr}  we discuss the limits of these approximations.
% and show that they are valid in the parameter space of interest for the VSI.
In particular we point out that the fully-radially-local approximation is only valid for
short cooling times, $\beta \lesssim O(1)${\bf, which is the 
  regime in which the VSI operates, as demonstrated below. 
  On the other hand, for 
  $\beta\gtrsim O(1)$, this approximation can introduce artificial
  instability due to the non-self-consistent neglect of global radial gradients.}

>>>>

 In Appendix \ref{global_corr}  we discuss the limits of these approximations.
% and show that they are valid in the parameter space of interest for the VSI.
In particular we point out that the fully-radially-local approximation is only valid for
short cooling times, $\beta \lesssim O(1)${\bf, which is the 
  regime in which the VSI operates, as demonstrated below. 
  On the other hand, for 
  $\beta\gtrsim O(1)$, this approximation can introduce artificial
  instability due to the non-self-consistent neglect of global radial gradients (see \S\ref{analytic_adia}).}

### 2015-07-08 numerical.tex
more reply edits

Surface modes are a well known feature of the VSI in finite vertical
domains \citepalias{nelson13, mcnally14}. \citetalias{barker15} show
that surface modes arise whether the surface is {\bf imposed (as in
  our models)} or natural (for disk models with a zero-density surface).
{\bf BL15 mention the interface between a disk's interior and corona
  as a physical site for surface modes develop. While surface modes in
  a vertically isothermal disk model are a genuine mathematical feature of the 
  problem defined by Eq. \ref{lin_all} and Eq. \ref{bc}, they are
  artificial in the sense that there is no natural choice for $\zmax$.
}

>>>>

Surface modes are a well known feature of the VSI in finite vertical
domains \citepalias{nelson13, mcnally14}. \citetalias{barker15} show
that surface modes arise whether the surface is {\bf imposed (as in
  our models)} or natural (for disk models with a zero-density surface).
{\bf BL15 mention the interface between a disk's interior and corona
  as a physical boundary that can trigger  surface modes. 
  Since our vertically isothermal models lack a surface, modes which
  depend on the adopted value of $\zmax$ are not physically meaningful.}
  %While surface modes in
  %a vertically isothermal disk model are a genuine mathematical feature of the 
  %problem defined by Eq. \ref{lin_all} and Eq. \ref{bc}, they are
  %artificial in the sense that there is no natural choice for $\zmax$.}
